Comparing R packages for calculation of persistent homology

### 2020-03-08 tdabench-paper/tdabench.Rmd
revised caption

\begin{widefigure}
  \centering
  \includegraphics[height=2in]{../Figures/Final_Figures/fig3.png}
  \caption{
    \textbf{Comparison of Rips complex persistent homology calculation as a function of feature dimension.}
    The x-axis represents the number of features in the point cloud, and y-axis represents average run time.
    Point cloud number was held constant and indicated by color.
    All Rips complexes were calculated on an 8 dimensional box.
    Panel 1. Comparing run times for TDAstats.
    Panel 2. Comparing run times for Dionysus.
    Panel 3. Comparing run times for GUDHI.
    Limited point clouds were tested for high dimensional features due to computational limits.
    Average runtime is presented as mean +/- standard deviation over 10 iterations.}
\label{fig:box}
\end{widefigure}

>>>>

\begin{widefigure}
  \centering
  \includegraphics[height=2in]{../Figures/Final_Figures/fig3.png}
  \caption{
    \textbf{Comparison of Rips complex persistent homology calculation as a function of feature dimension.}
    Average runtime (mean $\pm$ SD, $n=10$ iterations per data point) for various point cloud sizes (denoted by color) is plotted against calculated feature dimension and faceted by TDA libary.
    Persistent homology was calculated on a uniformly distributed random sample of points contained within a 1 unit, 8-dimensional cube.
    Computational limitations of calculating persistent homology for a large number of feature dimensions restricted point clouds to relatively small sizes.}
\label{fig:box}
\end{widefigure}
